From Freebase to Wikidata: The Great Migration

### 2015-10-15 paper.tex
Add precisions about the date-longitude propagation
(please review the English)

In order to get an idea of the coverage of the two knowledge bases,
we have further created a~spatio-temporal visualization of Freebase and Wikidata 
that is shown in \autoref{fig:time-space}.
The used method is to extract the earliest date and the longitude
linked to each of the entities of the two knowledge bases
and propagate them to the connected entities which do not have such data
using a~decreasing exponential distribution \todo{Please clarify the ``propagate'' part}.
We see that the two knowledge bases follow the same basic patterns,
with their coverage mostly concentrated on Europe and North America.
There are no strong differences between them,
yet coverage of \mbox{\emph{post}-year-2000} entities seems better in Freebase.
Our theory is that this is \emph{(i)}~due to the absence of a~lot of musical data in Wikidata
that in contrast is present in Freebase,
and \emph{(ii)} due to the US population CVTs in Freebase.
The big horizontal lines in \autoref{fig:freebase} and more even in \autoref{fig:wikidata}
can most probably be traced back to places that do not have any linked date,
and in consequence inherit the foundation date of their country.
For Wikidata (\autoref{fig:wikidata}), two lines that are definitely caused by this effect
are the big line over the USA around 1780
and the one covering Russia around 850.
One possible conclusion from this visualization could be that Wikidata,
despite its smaller absolute size, appears to have
a~nearly as complete coverage of the world as Freebase.
Nonetheless, it is very challenging to find objective ways to compare the two databases
and good metrics of success for the migration.
We certainly note that for knowledge bases the amount of triples is not an adequate measure
to judge the proportion of additional good data.

>>>>

In order to get an idea of the coverage of the two knowledge bases,
we have further created a~spatio-temporal visualization of Freebase and Wikidata 
that is shown in \autoref{fig:time-space}.
The used method is to extract the earliest date and the longitude
linked to each of the entities of the two knowledge bases
and propagate them to the connected entities which do not have such data.
To implement this propagation we set as value (date or longitude)
the average of the values of the entities which distance is less than $10$ with,
as weighting, $2^{-d}$ with $d$ the distance between the two entities.
We see that the two knowledge bases follow the same basic patterns,
with their coverage mostly concentrated on Europe and North America.
There are no strong differences between them,
yet coverage of \mbox{\emph{post}-year-2000} entities seems better in Freebase.
Our theory is that this is \emph{(i)}~due to the absence of a~lot of musical data in Wikidata
that in contrast is present in Freebase,
and \emph{(ii)} due to the US population CVTs in Freebase.
The big horizontal lines in \autoref{fig:freebase} and more even in \autoref{fig:wikidata}
can most probably be traced back to places that do not have any linked date,
and in consequence inherit the foundation date of their country.
For Wikidata (\autoref{fig:wikidata}), two lines that are definitely caused by this effect
are the big line over the USA around 1780
and the one covering Russia around 850.
One possible conclusion from this visualization could be that Wikidata,
despite its smaller absolute size, appears to have
a~nearly as complete coverage of the world as Freebase.
Nonetheless, it is very challenging to find objective ways to compare the two databases
and good metrics of success for the migration.
We certainly note that for knowledge bases the amount of triples is not an adequate measure
to judge the proportion of additional good data.
